\noindent
\subsection{WP5: Overtourism Management and Virtual Flow Control}

\textbf{Leading Partner:} Sorbonne Université (with strong involvement from Sapienza Università di Roma and NKUA for Mediterranean use-cases)

\textbf{Objectives and Concept:}
This Work Package directly addresses the pressing issue of mass tourism on vulnerable monuments in the Mediterranean and Atlantic regions. By establishing virtual alternatives, the physical burden on highly visited sites is reduced, and tourism flows can be diverted to lesser-known locations. This involves climate-sensitive digitization (e.g., coastal erosion monitoring) and utilizing the "Virtual-First" tourism model.

\textbf{Deliverables / Schedule (from Gantt chart):}
\begin{itemize}
    \item \textbf{D5.1 Development of a "Virtual-First" tourism model (remote access vs. on-site restrictions):} Year 2 (Month 1-6). The aim here is to create strategic guidelines that prioritize digital exploration for highly vulnerable sites while limiting physical entry. Researchers will analyze data from Mediterranean use-cases to determine optimal carrying capacities and define conditions where virtual access becomes the primary mode of visitation.
    \item \textbf{D5.2 Design of digital ticketing system and "capacity monitoring" algorithms:} Year 2 (Month 4-6). This involves developing software tools that dynamically control physical ticket availability based on real-time sensor data and site deterioration levels. The algorithm will automatically incentivize virtual tickets or reroute visitors to nearby, less burdened attractions during peak hours.
    \item \textbf{D5.3 Awareness campaign about the "responsible digital tourist" concept:} Year 2 (Month 7-9). A comprehensive communication strategy will be rolled out to educate the public on the environmental and cultural importance of reducing physical tourism footprints. Through targeted media and social platforms, the campaign will promote VR/AR tours as premium, sustainable alternatives rather than mere substitutes.
\end{itemize}