\noindent
\subsection{WP7: Economic Models and Revenue Generation}
\blocktitle{Leading Partner:} Springer Nature

\blocktitle{Objectives:} The primary objective of this Work Package is to establish a robust financial framework that ensures the project's self-sufficiency beyond the initial 24-month funding period. We aim to transform high-fidelity digital twins into viable economic assets for local communities and the consortium by creating diverse revenue streams.

\blocktitle{Duration:} Month 7-12

\blocktitle{Tasks:}

  \begin{itemize}
    \item \textbf{Task 7.1: Digital ticketing and subscription models (B2C):}
      
          Development of a tiered access system for the VR platform. This includes "Basic" (free educational access), "Premium" (high-resolution guided tours), and "Seasonal Pass" (access to all regional clusters).

    \item \textbf{Task 7.2: Development of a licensing framework for educational institutions and museums (B2B):}
     
          Designing a standardized licensing package for third-party stakeholders such as schools, universities, and international museums to use the VEP engine for their own curricula or exhibitions.

    \item \textbf{Task 7.3: Integrating local artisanal products and services into the virtual marketplace:}
     
          Creating a digital bridge between virtual visitors and local craftspeople. This involves an e-commerce layer within the XR experience allowing users to purchase physical goods from the CEE, Mediterranean, or Atlantic regions.
  \end{itemize}

\blocktitle{Deliverables:}

  \begin{itemize}
    \item \textbf{Deliverable 7.1: Comprehensive Business Sustainability Plan:}
      
        5-year financial projection including revenue streams and operational costs.

    \item \textbf{Deliverable 7.2: Standardized Licensing Agreement Template:}
     
        Legal documentation for B2B partnerships.
    \end{itemize}

\blocktitle{Milestones:}

  \begin{itemize}
    \item \textbf{Milestone 7:}
    
      Execution of the first commercial license agreement with a non-consortium educational entity (Month 20).

  \end{itemize}

\blocktitle{Geographical Relevance:} Revenue models will be tailored to regional strengths: emphasizing the "Digital Souvenir" market in the Mediterranean and "Cultural Educational Kits" in the CEE region.