\noindent
\subsection{WP8: Testing, Validation and Pilot Actions}
\blocktitle{Leading Partner:} Arts et Métiers (CAPLAB / Laval Virtual)

\blocktitle{Objectives:} This phase focuses on the technical and social validation of the developed prototypes. By deploying the platform in diverse geographic settings, we ensure the technology is resilient to varying environmental factors and user backgrounds, while measuring the actual impact on physical site preservation.

\blocktitle{Duration:} Month 4-12

\blocktitle{Tasks:}

  \begin{itemize}
    \item \textbf{Task 8.1: Implementation of Multi-Regional Pilot Events:}
    
    Organizing four physical and virtual "Launch Days" across the Atlantic (focusing on coastal erosion sites), Mediterranean (ancient ruins), and CEE (castles and wooden churches).

    \item \textbf{Task 8.2: Technical Performance and Stress Testing:}
     
    Evaluating rendering performance across different devices (from high-end VR headsets to mobile AR) and network bandwidth conditions.

    \item \textbf{Task 8.3: Comprehensive User Feedback Collection:}
     
    Utilizing User Experience (UX) research methods, including eye-tracking during VR sessions and qualitative focus groups with diverse age demographics to refine the interface.
  \end{itemize}

\blocktitle{Deliverables:}

  \begin{itemize}
    \item \textbf{Deliverable 8.1: Pilot Evaluation Report:}
      
        A technical summary of the performance metrics and bug reports gathered during the pilots.

    \item \textbf{Deliverable 8.2: Social Impact and UX Assessment:}
     
        Detailed analysis of how the virtual experience shifted visitor attitudes toward physical site conservation.
    \end{itemize}

\blocktitle{Milestones:}

  \begin{itemize}
    \item \textbf{Milestone 8:}
    
      Successful completion of all four regional pilot actions with a minimum 85\% positive user satisfaction rate (Month 22).

  \end{itemize}

\blocktitle{Geographical Relevance:} Testing will address specific regional challenges, such as high-glare lighting conditions for AR in Greece and hardware resilience in high-humidity Atlantic environments.