\noindent
\subsection{WP9: Sustainability, Dissemination and Communication}

\blocktitle{Leading Partner:} Springer Nature

\blocktitle{Objectives:} Following the \textbf{CHARM-EU} model of long-term alliance strategy, this WP focuses on the post-project life cycle. It ensures the alliance remains sustainable through the repurposing of existing resources, the establishment of a permanent legal identity, and the wide dissemination of scientific results.

\blocktitle{Duration:} Month 1-12

\blocktitle{Tasks:}

  \begin{itemize}
    \item \textbf{Task 9.1: Scientific Dissemination and Open Science:}
    
    Authoring peer-reviewed publications and presenting at international heritage and technology conferences (e.g., EuroVR, Digital Heritage).

    \item \textbf{Task 9.2: Closing Conference and "Virtual-Europe" Exhibition:}
     
    A flagship event in Brussels to showcase the project results to EU policymakers, demonstrating how XR can mitigate overtourism.

    \item \textbf{Task 9.3: Exploitation Plan and Long-Term Alliance Strategy:}
     
    Developing the "Long-term strategy for sustainability of the alliance." This includes exploring the creation of a separate legal entity (e.g., an AISBL) to manage IP and maintain the digital repository beyond the pilot phase.
  \end{itemize}

\blocktitle{Deliverables:}

  \begin{itemize}
    \item \textbf{Deliverable 9.1: Final Sustainability and Exploitation Plan:}
      
        A detailed roadmap for the alliance's activities for the next 10 years, including financial commitments from each member.

    \item \textbf{Deliverable 9.2: Communication Toolkit:}
     
        A package of branding materials and media assets for regional partners to ensure consistent messaging.
    \end{itemize}

\blocktitle{Milestones:}

  \begin{itemize}
    \item \textbf{Milestone 9:}
    
    Final Dissemination Event and publication of the VEP White Paper on Digital Heritage Policy (Month 24).

  \end{itemize}

\blocktitle{Sustainability Strategy (Alliance Specifics):}

\noindent In line with the strategy of the alliance, members are committed to action beyond the project lifecycle. This involves:

\begin{itemize}
    \item \textbf{Repurposing existing consortium resources} to ensure continuity without requiring significant new budget requirements.
    \item \textbf{Investigating legal formulas} (such as a separate legal identity) to overcome bureaucratic or management barriers to long-term cooperation.
    \item \textbf{Leveraging existing national and European grants} to support ongoing student and researcher mobility between the Mediterranean, Atlantic, and CEE partner regions.
  \end{itemize}