The "Virtual-Europe-Path" project (Digital Preservation of Cultural Heritage using XR Technologies) addresses the critical dual challenge of preserving Europe's deteriorating cultural monuments while managing the damaging physical impact of mass tourism. Current state-of-the-art digital preservation is often restricted to isolated, indoor environments and lacks the scalability required for complex outdoor archaeological sites [State of the Art]. This project advances the field by creating a pan-European, interdisciplinary framework that integrates high-fidelity 3D/4D scanning, eXtended Reality (XR), and Open Science principles to ensure the survival and accessibility of our shared heritage.

Led by Eötvös Loránd University, the consortium unites a world-class network of technological, publishing, and scientific partners:
\begin{itemize}
    \item \textbf{Technological Innovation: Arts et Métiers (CAPLAB)} shifts advanced 4D reality capture—originally developed for industrial and healthcare sectors—into the cultural heritage domain, recording not just structures but also "craftsman intelligence" through motion and gesture capture.
    \item \textbf{Scientific Dissemination: Springer Nature} drives a high-impact Open Access model, transforming project data into a global "fuel" for researchers, startups, and museums.
    \item \textbf{Regional Expertise}: Premier institutions including Sapienza Università di Roma, NKUA (Athens), ELTE (Budapest), and Sorbonne Université provide the archaeological anchor, testing these technologies across diverse and complex scenarios—from Roman urban ruins and Greek coastal sanctuaries to Central European endangered wooden churches and Atlantic fortifications.
\end{itemize}

\textbf{Key Outcomes and Innovations}
\begin{itemize}
    \item \textbf{"Virtual-first" Tourism Model}: Mitigating overtourism by providing remote, high-fidelity XR experiences that serve as "experience replicas" for fragile or restricted sites.
    \item \textbf{Technological Validation}: Pushing 3D/4D scanning tools to higher Technology Readiness Levels (TRL) through validation in deteriorating outdoor environments and climatic risk zones.
    \item \textbf{Economic and Social Impact}: Establishing a sustainable ecosystem through digital ticketing, virtual marketplaces for local artisans, and community-led narratives that preserve local identity.
\end{itemize}

By bridging the gap between scientific documentation and immersive public access, "Virtual-Europe-Path" creates a scalable, standardized workflow for the digital era, ensuring that Europe's cultural legacy is both physically protected and globally accessible.