The total estimated budget for the \textbf{"Virtual-Europe-Path"} project is \textbf{€4,000,000}, distributed over a \textbf{24-month} duration. This budget is strategically allocated to support high-fidelity data acquisition, cutting-edge XR development, and a robust Open Science dissemination framework.

\textbf{Budget Breakdown by Work Package (WP)}
The allocation reflects the high costs of technical infrastructure in the scanning phase and the development of the VR/AR engine.
\begin{table}[h!]
    \centering
    \caption{Budget Breakdown by Work Package (WP)}
    \label{tab:wp_budget}
    \begin{tabular}{|l|p{5cm}|r|p{5cm}|}
        \hline
        \textbf{WP \#} & \textbf{Work Package Title} & \textbf{Budget (€)} & \textbf{Primary Cost Drivers} \\ \hline
        WP1 & Management of the project & 280,000 & Admin staff at UBB, QA, and Risk management. \\ \hline
        WP2 & Methodology \& Site Selection & 320,000 & Stakeholder analysis and vulnerability indexing. \\ \hline
        WP3 & Data Acquisition \& 3D Scanning & 1,000,000 & LiDAR equipment, drone operations in complex terrain. \\ \hline
        WP4 & XR Platform Development & 800,000 & Software engineering and 4D reality capture. \\ \hline
        WP5 & Overtourism Management & 320,000 & Capacity monitoring algorithms. \\ \hline
        WP6 & Community Engagement & 320,000 & Field workshops and social impact assessment. \\ \hline
        WP7 & Economic Models \& Revenue & 280,000 & Licensing frameworks and virtual marketplace. \\ \hline
        WP8 & Testing \& Validation & 400,000 & Pilot events and technical validation. \\ \hline
        WP9 & Dissemination \& Communication & 280,000 & Open Access APC fees and final exhibition. \\ \hline
        \textbf{Total} & & \textbf{4,000,000} & \\ \hline
    \end{tabular}
\end{table}

\textbf{Partner Budget Allocation (Estimated Shares)}
Budget shares are distributed based on the technical intensity of tasks and regional leadership roles.
\begin{itemize}
    \item \textbf{Babeș-Bolyai University (UBB) - Coordinator (€550,000)}: Focuses on overall project management, administrative costs, and coordinating CEE site selection.
    \item \textbf{Arts et Métiers (CAPLAB) (€850,000)}: Receives the largest share for XR platform development, 4D reality capture, and technology validation.
    \item \textbf{Springer Nature (€400,000)}: Allocated funds for managing the Open Access ecosystem, publication fees (APC), and data platform value enhancement.
    \item \textbf{Sapienza (Italy) (€550,000)}: Field scanning of urban ruins and overtourism social mission.
    \item \textbf{NKUA (Greece) (€550,000)}: Outdoor scanning in complex terrains and climate risk documentation.
    \item \textbf{ELTE (Hungary) (€550,000)}: AI-based processing and "Danube-AI" digital humanities integration.
    \item \textbf{Sorbonne Université (€550,000)}: Coordination of high-fidelity data collection and Atlantic erosion studies.
\end{itemize}

\textbf{Detailed Cost Categories}
\begin{table}[h!]
    \centering
    \caption{Detailed Cost Categories}
    \label{tab:cost_categories}
    \begin{tabular}{|l|p{4cm}|p{7cm}|}
        \hline
        \textbf{Category} & \textbf{Estimated (€)} & \textbf{Justification} \\ \hline
        Personnel & 2,600,000 & Researchers, XR engineers, and administrative coordinators across 4 regions. \\ \hline
        Travel \& Subsistence & 300,000 & Fieldwork for scanning at remote sites and international consortium meetings. \\ \hline
        Equipment & 500,000 & LiDAR, high-performance drones, and VR/AR hardware for pilots. \\ \hline
        Other Goods \& Services & 400,000 & Open Access publication fees (APC), licenses, and final exhibition costs. \\ \hline
        Indirect Costs (25\%) & 200,000 & Standard EU overhead for institutional infrastructure. \\ \hline
        \textbf{Total} & \textbf{4,000,000} & \\ \hline
    \end{tabular}
\end{table}

\textbf{Budgetary Synergy and Efficiency}
The budget utilizes Springer Nature's Open Access model to ensure that publication costs (APC) result in higher citation rates and broader societal impact, justifying the dissemination spend. Technological costs are optimized by using Arts et Métiers' existing CAPLAB infrastructure, which is upgraded through the project rather than built from scratch.
