\noindent
The "Virtual-Europe-Path" consortium is a strategically assembled group of world-class academic institutions, a leading technology center, and a global scientific publisher. This interdisciplinary team spans across Europe, covering the Mediterranean, Atlantic, and Central-Eastern regions to address the preservation of cultural heritage through eXtended Reality (XR).

\textbf{Technology Pillar: Arts et Métiers (CAPLAB / Laval Virtual)}
As the primary technology partner, Arts et Métiers serves as a European hub for XR, Digital Twins, and 3D technologies.
\begin{itemize}
    \item \textbf{Core Expertise}: The CAPLAB platform specializes in 4D reality capture, which includes the recording of movement, gestures, sound, and physiological data.
    \item \textbf{Project Role}: They provide the technical framework for "craftsman intelligence" and knowledge preservation.
    \item \textbf{Strategic Benefit}: The project allows them to validate their technologies in complex, real-world outdoor environments—such as archaeological ruins—thereby increasing their Technology Readiness Level (TRL).
\end{itemize}

\textbf{Dissemination and Open Science Pillar: Springer Nature}
Springer Nature, one of the world's largest scientific publishers, acts as the bridge between research and global visibility.
\begin{itemize}
    \item \textbf{Core Expertise}: They focus on Open Access, Open Science, and digital research ecosystems.
    \item \textbf{Project Role}: They manage the high volume of publications, datasets, and case studies generated by the project's interdisciplinary nature.
    \item \textbf{Strategic Benefit}: By utilizing an Open Access revenue model, they ensure that research reaches a wide audience including museums, startups, and developers.
\end{itemize}

\textbf{Mediterranean Region: Sapienza Università di Roma and NKUA}
This axis represents the most densely layered and vulnerable heritage in Europe.
\begin{itemize}
    \item \textbf{Sapienza Università di Roma}: Founded in 1303, its Department of Antiquities is a global leader in classical archaeology and monument preservation. They bring expertise in urban heritage documentation and interdisciplinary preservation theories involving law and ethics. Their involvement focuses on high-traffic sites like the Forum Romanum to test "experience replicas" as a solution to overtourism.
    \item \textbf{National and Kapodistrian University of Athens (NKUA)}: Greece's oldest university provides expertise in monitoring outdoor ruins, such as acropolises and coastal sanctuaries. They lead the study on coastal erosion and climatic risks, providing a critical outdoor testing environment for 3D/4D scanning technology.
\end{itemize}

\textbf{Central and Eastern Europe (CEE): Eötvös Loránd University (ELTE)}
The CEE region focuses on endangered castles, manor houses, and wooden churches.
\begin{itemize}
    \item \textbf{ELTE BTK}: The Institute of Archaeological Sciences is a pioneer in non-destructive research and digital archaeology in Hungary.
    \item \textbf{Specialized Units}: The Department of Digital Humanities and the National Laboratory for Digital Heritage lead the AI-based processing of cultural assets.
    \item \textbf{Project Role}: They manage the "Danube-AI" initiative, applying Machine Learning tools to heritage along the Danube.
\end{itemize}

\textbf{Atlantic Coast Region: Sorbonne Université}
This region focuses on coastal fortifications and lighthouses threatened by erosion.
\begin{itemize}
    \item \textbf{Sorbonne Université (Faculté des Lettres)}: Their Institute of Art and Archaeology is a center for researching medieval and early modern fortification systems.
    \item \textbf{Project Role}: They are responsible for leading the data collection work package, ensuring standardized protocols across all regions.
\end{itemize}

\textbf{Strategic Network Expansion: University of Bologna (Unibo)}
The consortium remains open to integrating the University of Bologna to further strengthen the medieval heritage focus. Through their FrameLab project, Unibo offers top-tier European expertise in heritage digitization and medieval studies, adding depth to the project's historical scope.