The dissemination strategy for the "Virtual-Europe-Path" project is designed to maximize the visibility, uptake, and scientific impact of the research outcomes across academic, industrial, and public sectors. By leveraging the unique strengths of our publishing partner, Springer Nature, and the technological expertise of Arts et Métiers (CAPLAB), the project ensures that its findings are accessible to the widest possible audience.
\subsection{Academic and Scientific Dissemination}
The primary vehicle for scientific dissemination is a robust Open Access publication strategy. This approach ensures that research remains freely accessible while maintaining high citation potential and visibility.
\begin{itemize}
    \item \textbf{Open Access Publications}: High-quality, interdisciplinary articles will be published in journals such as Heritage Science and Open Access.
    \item \textbf{Open Science Ecosystem}: Beyond traditional articles, the project will release primary research data, including 3D models, scanning datasets, and VR assets, as part of an open research framework.
    \item \textbf{Conference Participation}: Partners such as NKUA and Sapienza will present findings at international archaeology and digital heritage conferences to strengthen their positions within EU innovation networks.
    \item \textbf{Thematic Cohesion}: Collaborative publications between regional partners (e.g., Sapienza and NKUA) will highlight comparative studies of Mediterranean heritage, increasing the thematic impact of the project.
\end{itemize}

\subsection{Technological and Industrial Dissemination}
To foster innovation and market potential, the project targets developers and the tech industry.
\begin{itemize}
    \item \textbf{Technology Validation}: The project acts as a live validation for XR technologies in complex outdoor environments, increasing the Technology Readiness Level (TRL) of the platforms used.
    \item \textbf{Developer and Startup Engagement}: By highlighting new XR use cases in cultural heritage, the project attracts interest from software developers and startups specializing in VR/AR applications.
    \item \textbf{Technology Transfer}: Arts et Métiers will utilize the project to demonstrate the practical application of 4D reality-capture, facilitating knowledge transfer to industrial and cultural partners.
\end{itemize}

\subsection{Stakeholder and Public Engagement}
Dissemination extends to the "end-users" of cultural heritage: museums, tourism boards, and the general public.
\begin{itemize}
    \item \textbf{Professional Networks}: Results will be shared with national and international heritage bodies, such as the Italian Ministry of Culture (MiC) and UNESCO, to inform future monument preservation strategies.
    \item \textbf{Virtual Heritage Exhibition}: A dedicated exhibition will be organized to showcase the VR/AR prototypes to the public, demonstrating the "Virtual-first" tourism model.
    \item \textbf{"Virtual-Europe-Path" Closing Conference}: A final event will gather all stakeholders to discuss the project's social impact and its role in reducing overtourism through digital alternatives.
\end{itemize}

\subsection{Expoitation and Sustainability Plan}
The project includes a structured Exploitation Plan to ensure long-term viability beyond the initial funding period.
\begin{itemize}
    \item \textbf{Standardization of Data}: The project will produce standardized 3D models and documentation protocols that can be adopted by other regions to create a consistent European digital heritage database.
    \item \textbf{Brand Positioning}: For partners like Springer Nature, the project serves to position the organization as a comprehensive knowledge platform for EU-funded research.
    \item \textbf{Scalability}: The methodologies developed in the Mediterranean, Atlantic, and CEE regions are designed to be adaptable to other heritage sites globally, ensuring a lasting technological legacy.
\end{itemize}