\textbf{Project Topic and Correlation with the Call}\\
The project, "Digital Preservation of Cultural Heritage using XR Technologies," focuses on the high-fidelity digital reconstruction and immersive accessibility of endangered cultural monuments. By integrating 3D laser scanning (LiDAR), aerial photogrammetry, and Extended Reality (XR)—comprising Virtual, Augmented, and Mixed Reality—the proposal creates "digital twins" of historical sites. This aligns with the thematic priorities of the call by fostering technological innovation in the preservation of European cultural identity across Mediterranean, Central-Eastern European, and Atlantic regions.

\medskip
\textbf{Practical Relevance}\\
The practical relevance of this research addresses two critical global challenges: the physical degradation of heritage sites caused by environmental factors (e.g., coastal erosion, climate change) and the unsustainable pressure of mass tourism. The project offers a non-destructive preservation method, allowing for the meticulous recording of structures before further decay occurs. Furthermore, it provides a scalable solution for "Virtual-First" tourism, which unburdens fragile UNESCO sites while maintaining economic engagement through digital accessibility.

\medskip
\textbf{End-Products and Expected Results}\\
The project will deliver a suite of integrated technological solutions:
\begin{itemize}
    \item \textbf{Standardized Digital Heritage Framework:} 
    A methodological protocol for high-precision 3D documentation in complex outdoor environments.
    \item \textbf{VR-based "Virtual Tour" Engine:}
    A high-fidelity rendering architecture (Unreal/Unity) capable of handling massive photogrammetry datasets for remote exploration.
    \item \textbf{AR-based "On-Site Time Machine":}
    A mobile module that overlays digital reconstructions onto real-world ruins in real-time for physical visitors.
    \item \textbf{Open Science Ecosystem:}
    A cloud-based repository for 3D assets and scientific documentation, ensuring long-term visibility and research integration.
\end{itemize}

\medskip
\textbf{Success Criteria}\\
Success will be measured by the advancement of Technology Readiness Levels (TRL) through validation in real-world ruin scenarios. Key performance indicators include a minimum 85% positive user satisfaction rate during regional pilot actions and the execution of commercial licensing agreements for the developed platform.
