\textbf{P1 – Eötvös Loránd University (ELTE)}
\begin{itemize}
  \item \textbf{Team Leader:} Dr. Hősi Rezső Rudolf
  \item \textbf{Key Person:} Oláh Sára (Lead Developer \& UX Strategist)
    \begin{itemize}
      \item \textbf{Role:} Oversees the "Danube-AI" integration and the user-centric design of the XR platform.
      \item \textbf{Experience:} Expert in digital archaeology and AI-based heritage processing.
      \item \textbf{Achievements:}
      \begin{enumerate}
        \item UI/UX design for the National Laboratory for Digital Heritage.
        \item Coordination of the "Digital Humanities" project branch.
      \end{enumerate}
    \end{itemize}
  \item \textbf{Additional Staff:} 2 AI Engineers (MI-based processing), 1 Archaeologist (Digitization expert), 2 PhD Students (Data collection).
\end{itemize}

\noindent
\textbf{P2 – Arts et Métiers (CAPLAB / Laval Virtual)}
\begin{itemize}
  \item \textbf{Team Leader:} Prof. Dr. Jean-Luc Soulié
  \item \textbf{Team Structure:} 
    \begin{itemize}
      \item 1 \textbf{4D Capture Specialist} (Knowledge and gesture preservation).
      \item 2 \textbf{XR Engineers} (VR/AR platform development).
      \item 2 \textbf{Field Technician} (Outdoor/complex environment scanning).
    \end{itemize}
\end{itemize}

\noindent
\textbf{P3 – Springer Nature}
\begin{itemize}
  \item \textbf{Team Leader:} Dr. Helen Zhang
  \item \textbf{Team Structure:} 
    \begin{itemize}
      \item 1 \textbf{Open Access Coordinator} (APC and licensing management).
      \item 1 \textbf{Data Scientist} (3D model and dataset repository).
      \item 1 \textbf{Brand Manager} (Reputation and social impact).
    \end{itemize}
\end{itemize}

\noindent
\textbf{P4 – Sapienza Università di Roma}
\begin{itemize}
  \item \textbf{Team Leader:} Prof. Giulia Rossi
  \item \textbf{Team Structure:} 
    \begin{itemize}
      \item 2 \textbf{Classical Archaeologists} (Roman urban history).
      \item 1 \textbf{Digital Documentation Expert} (Scanning and photogrammetry).
      \item 1 \textbf{Legal\/Ethical Consultant} (Heritage theory).
    \end{itemize}
\end{itemize}

\noindent
\textbf{P5 – National and Kapodistrian University of Athens (NKUA)}
\begin{itemize}
  \item \textbf{Team Leader:} Prof. Dr. Dimitri Papadopoulos
  \item \textbf{Team Structure:} 
    \begin{itemize}
      \item 1 \textbf{Environmental Monitoring Expert} (Climate risk analysis).
      \item 1 \textbf{Byzantine Archaeology Specialist}.
      \item 1 \textbf{GIS and Mapping Technician} (Outdoor site modeling).
    \end{itemize}
\end{itemize}

\noindent
\textbf{P6 – Sorbonne Université}
\begin{itemize}
  \item \textbf{Team Leader:} Dr. Claire Lefebvre
  \item \textbf{Team Structure:} 
    \begin{itemize}
      \item 2 \textbf{Architectural Historians} (Medieval fortifications).
      \item 1 \textbf{Data Collection Coordinator} (Atlantic region lead).
      \item 1 \textbf{Research Assistant} (Comparative regional data).
    \end{itemize}
\end{itemize}