\noindent
The project is structured into the following work packages:

\begin{itemize}
    \item WP1: Project management and coordination
    \item WP2: Data collection and fieldwork
    \item WP3: XR development and integration
    \item WP4: XR Platform Development and UX Design (Lead: Arts et Métiers - CAPLAB / Laval Virtual) - This work package is dedicated to the technical realization and validation of the project's digital ecosystem. By leveraging the CAPLAB platform's advanced 4D reality capture capabilities—including the high-frequency recording of motion, gestures, and physiological data—the project aims to preserve not just the physical structures but also the "craft intelligence" (intangible knowledge and manual movements) associated with heritage sites.
    \begin{itemize}
        \item \textbf{Task 4.1: Development of an Interdisciplinary VR Engine.} Utilizing state-of-the-art rendering environments (Unreal/Unity), this task develops a "Virtual Tour" framework optimized for massive 3D datasets.
        \item \textbf{Task 4.2: UX Research and Cognitive Impact Analysis.} Measuring the "experiential value" and pedagogical effectiveness of XR through focus groups and biometric feedback.
        \item \textbf{Task 4.3: Technology Validation and TRL Elevation.} Moving AR reconstruction from laboratory settings to complex outdoor environments to increase the Technology Readiness Level.
    \end{itemize}
    \item WP5: Overtourism Management and Virtual Flow Control (Lead: Sorbonne Université) - WP5 establishes a strategic response to the physical deterioration of heritage sites by managing visitor pressure through digital alternatives. It aligns with EU priorities for sustainable tourism by establishing a "Virtual-First" model that balances remote digital access with physical preservation requirements.
    \begin{itemize}
        \item \textbf{Task 5.1: "Virtual-First" Tourism Architecture.} Developing a remote access model that serves as a high-quality substitute for physical visits in sensitive areas.
        \item \textbf{Task 5.2: Intelligent Capacity Monitoring and Flow-Control Algorithms.} Designing digital ticketing systems integrated with real-time visitor flow algorithms to regulate attendance.
        \item \textbf{Task 5.3: Responsible Digital Citizenship and Awareness.} Launching an awareness campaign to promote the ethical use of digital heritage and its link to physical preservation.
    \end{itemize}
    \item WP6: Community Engagement and Social Impact (Lead: ELTE BTK) - Managed by the Digital Heritage National Lab, this work package utilizes AI-based processing to weave digitized assets into the social fabric of local communities. It focuses on co-creation processes to ensure that technological innovation translates into tangible social benefits and strengthened local identities.
    \begin{itemize}
        \item \textbf{Task 6.1: Socio-Digital Identity Workshops.} Organizing community-driven events to ensure that digital twins reflect local stakeholders' identity.
        \item \textbf{Task 6.2: Intangible Heritage Co-Creation and XR Narratives.} Integrating local legends and oral histories into the XR experience through collaborative scripting.
        \item \textbf{Task 6.3: Advanced Social Impact Assessment (SIA).} Utilizing the "Danube-AI" methodology to evaluate long-term effects on local cohesion and tourism patterns.
    \end{itemize}
\end{itemize}

A detailed timeline (Gantt chart) will define milestones and deliverables across the project duration.