\documentclass[../main.tex]{subfiles}

\begin{document}

\subsection{The Rise of "Vibe Coding" and AI-Assisted Development}

The rapid advancement of Large Language Models (LLMs) has initiated a significant paradigm shift in software engineering and computing education.
By generating functional code from natural language descriptions, these AI tools have drastically lowered the barrier to entry for programming.
This technological leap has given rise to a new programming paradigm colloquially known as "vibe coding". 
In vibe coding, developers express their software ideas in natural language, relying on the AI to interpret these high-level intents and generate the corresponding executable code.
This approach shifts the developer's role from a traditional coder focused on syntactic precision to a conceptual guide.
While this democratization expands access to computational tools for non-experts, 
it fundamentally alters the cognitive demands of programming, shifting the human effort from writing code to reading, comprehending, evaluating, and repairing AI-generated outputs.
\cite{fortes2025vibe}, \cite{kazemitabaar2023studying}, \cite{lau2023from} 

\subsection{The Research Problem: Debugging as the Critical Bottleneck}

Although vibe coding significantly accelerates the initial code generation phase, it introduces severe challenges later in the software development lifecycle, particularly for novices.
We identify this core issue as the "Debugging Paradox": the very tools that provide a fast initial start ultimately leave beginners helpless when the AI-generated code contains complex, undocumented, architectural, or logical errors.
While LLMs excel at fixing superficial syntax errors, debugging requires a deep validation of the causal relationships between the code and the overall system logic.
Because the students did not construct the code step-by-step through their own cognitive effort, they lack the essential prior knowledge and structural understanding required to troubleshoot it.
Consequently, when the AI hallucinates, generates incorrect control flows, or fails to resolve an environment-specific issue (e.g., a dependency mismatch), students are left stranded with a codebase they do not understand, leading to frustration and an inability to manually resolve the problem.
\cite{prather2024widening}

\subsection{Research Objectives and Hypotheses}

To systematically investigate the "Debugging Paradox" and understand how vibe coding affects novice programmers' cognitive processes and problem-solving resilience, this study proposes eight hypotheses.
These hypotheses are categorized into three core dimensions of the AI-assisted software development lifecycle.

\subsubsection{Learning Phase and Cognitive Integrity}

  \begin{itemize}
    \item \textbf{H1 (Superficial Learning):}
          Novice programmers using AI tools bypass the explicit, deep learning phase.
          By utilizing the AI as a shortcut, they fail to engage in the authentic problem-solving processes required for skill acquisition.

    \item \textbf{H2 (Lack of Comprehension):}
          Students frequently utilize AI-generated code without understanding its underlying mechanics.
          Uncritical acceptance leads to an inability to recognize even basic structural errors, such as infinite loops, within their own code.

    \item \textbf{H6 (The Prompt-Looping Anti-Pattern):}
          When the AI fails or makes an error, students disproportionately attempt to bypass the issue with new prompts ("prompt-looping") rather than manually reading and interpreting the codebase.
  \end{itemize}

\subsubsection{Debugging Dynamics and Interaction}

  \begin{itemize}
    \item \textbf{H3 (Debugging Inability):}
          Due to superficial learning (H1) and a lack of comprehension (H2), students are left unequipped to identify and fix bugs.
          This becomes especially evident when dealing with superficially functional but logically fragile "house of cards" code generated by AI.

    \item \textbf{H4 (Over-Reliance):}
          Novice programmers fall into the trap of blind trust and over-reliance on AI-generated solutions.
  \end{itemize}

\subsubsection{Competence Gap and Systems Thinking}

  \begin{itemize}
      \item \textbf{H5 (Architectural Confusion):}
           As application size and complexity increase, beginners lacking background knowledge struggle to integrate independently generated AI snippets.
           This results in an inconsistent and fragile "patchwork codebase".

      \item \textbf{H7 (Absence of Mental Models):}
          Complete cognitive offloading to AI prevents the formation of a coherent mental model of the code.
          Consequently, students are rendered incapable of identifying and manually validating complex, intentionally placed errors (e.g., outdated library dependencies).

      \item \textbf{H8 (Skill-Based Divide):}
          Programmers with better foundational skills and higher self-efficacy recognize AI limitations earlier, abandon prompt-looping, and successfully transition to manual debugging.
          In contrast, weaker students exhibit over-reliance and prematurely abandon the task.
  \end{itemize}

\end{document}
