\documentclass[../main.tex]{subfiles}

\begin{document}

Data collected during the experiment were analyzed to test our 8 hypotheses (H1-H8), 
which we categorized into three logical clusters based on the software development lifecycle.

\subsection{Learning Phase and Cognitive Integrity (H1, H2, H6)}
\begin{itemize}
    \item \textbf{H1-H2 (Cognitive Erosion)}: The data strongly supported the hypothesis that "vibe coding" causes learners to skip line-by-line interpretation of their code, 
    fundamentally hindering deep learning. Participants who fully delegated coding tasks to the AI bypassed the essential cognitive struggle required to form new skills, 
    resulting in impaired conceptual understanding, diminished code-reading abilities, and a significant reduction in overall knowledge retention. 
    Those employing an "AI Delegation" interaction pattern demonstrated the lowest levels of independent thinking and cognitive engagement. \cite{shen2026how}
    \item \textbf{H6 (The Role of Prior Knowledge)}: Conversely, developers with stronger prior manual programming experience proved much faster at recognizing the AI's limitations. 
    Higher-competence programmers evaluate AI-generated code more critically—actively reviewing, debugging, and striving to understand it. Rather than relying on the AI to 
    generate complete solutions, these experienced students used the tool as a "lifesaver" for conceptual inquiry and clarification, which preserved their learning outcomes 
    and protected them from cognitive erosion. \cite{kusper2025we} \cite{shen2026how}
\end{itemize}

\subsection{Debugging Phase and Interaction Dynamics (H3, H4)}
\begin{itemize}
    \item \textbf{H3-H4 (The Debugging Trap)}: The experimental group exhibited a strong tendency to fall into an endless "prompt-loop" 
    rather than reading error messages or engaging in manual code inspection. This behavior, categorized as "Iterative AI Debugging," 
    involves students repeatedly throwing the same error back to the AI assistant for troubleshooting. By relying on the AI to blindly 
    verify and fix code, participants avoided manual code reading and failed to clarify their own understanding of the root cause, which 
    ultimately correlated with poor performance and slower completion times. \cite{shen2026how}
    \item \textbf{Metacognitive Monitoring}: Participants severely misjudged their own progress based on the sheer volume of code the 
    AI was able to quickly generate. This created a new metacognitive difficulty known as "Progression," where students fell conceptually 
    behind the material but remained entirely unaware of it due to a false sense of confidence. The AI's rapid output provided an 
    "illusion of progress" and an unwarranted "illusion of competence" that masked their inability to actually solve the underlying 
    problem. \cite{prather2024widening}
\end{itemize}

\subsection{Competence Gap and Systems Thinking (H5, H7, H8)}
\begin{itemize}
    \item \textbf{H5 (Architectural Blindness)}: The data revealed that heavy reliance on vibe coding leads to a dangerous architectural blindness. Because developers piece 
    together code generated on-the-fly from isolated natural language prompts, they fail to grasp the deeper dependencies between modules. Without proper upfront design, the 
    resulting software resembles a "patchwork" of disconnected solutions or a "house of cards" that may function superficially but harbors critical structural deficiencies. \cite{maes2025gotchas} \cite{}
    \item \textbf{H7-H8 (Over-reliance)}: Finally, excessive reliance on generative AI was shown to directly correlate with a decrease in critical thinking and logical 
    inference. As users place higher trust and confidence in GenAI tools, they perceive a reduced need to exert cognitive effort, leading to a noticeable drop in critical 
    evaluation. When the AI generated misleading or incorrect suggestions, overly reliant students were easily led down the wrong logical path and lacked the foundational 
    understanding required to validate the AI's output or debug the resulting errors. \cite{lee2025impact} \cite{shen2026how} \cite{prather2024widening}
\end{itemize}

\end{document}
